---
title: "Alcohol vs Seat choice"
author: "Jennifer Espinoza Barrera"
date: "Summer 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
Based on the bloxplt the median of people who sit in the back consume the most alcohal than the others we can see that it looks higher than both the quartile ofpeople that sit in the front and the third quartile of those who sit in the middle.
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The third quantile of the front is 2 and the third quantile of the middle is 3. The median of the back is 4 so this means that the median of the back is higher than the third quantile of both the front and middle.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

After running the Inferential test we found that the probability of the poelpe in the front  and middle consum the same amount of alcohol as the poeple in the back being 0.000116.Therefore there is a significant difference between the 3.

```{r}
plot(TukeyHSD(model1))
```

When looking at the model we see that the middle compared to the back does not have 0 in thier confidence interval. The same is true when you compare the front and the back. this also shows that there is no satisfactical difference between the front and the middle. The back is different from everybody else. 

## Conclusions

When going through the process with more
than two variables there are more steps that we have to go through which can
complicate the process.In this assignment we used ggplot to create our boxplot which showed us the median of how many drinks were consumed per section. Then we ran a Numerical summary of the information so that we could get exact numbers and see how big the difference was. After this we ran the Inferential test to get the probability of these three sections consuming the same amount of alcohol which was 0.000116. We then used a comparison model that showed us how significant the difference between each section was.I have came to the conclusion that there is a significant difference between howmuch alcohol the three sections consumed.
